---
title: "Assignment_2Exercise"
author: "Xinyi Wang"
date: "9/19/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

###1.What happens if you facet on a continuous variable?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy)) +
  facet_wrap(~ displ)
```
You'll get one facet for each unique value of the variable.

###2.What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_grid(drv ~ cyl)
```

Empty cells in facet_grid imply that there were no rows with that combination of values in the original dataset. In this plot, rear wheel drive(r) with 4 or 5 cylinder(cyl) is missing, and 4 wheel drive(4) with 5 cylinder(cyl) is missing.

###3.What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

. acts a placeholder for no variable so that we can have a facet in only one dimension.

###4.Take the first faceted plot in this section:
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

Advantage of using faceting: Easier to examine the indivual classes.
Disadvantage of using faceting: Easier to see how the classes are clustered overall.
With larger datasets it’s more likely to use colour asethetic to see the overall clustering instead of the individual point clouds.

###5.Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?

nrow: number of rows
ncol: number of columns
e.g. scales：should Scales be fixed ("fixed", the default), free ("free"), or free in one dimension ("free_x", "free_y").
facet_grids() do not have these configuration because the rows and cols are determined by the specified attributes.

###6.When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?

This will extend the plot vertically, where you typically have more viewing space. If you extend it horizontally, the plot will be compressed and harder to view.












